Using Monte Carlo to estimate the effects of NHL rule changes

### 2020-12-10 slides.Rmd
got rid of errors

---
title: "Using Monte Carlo to estimate the effects of NHL rule changes"
author: "Kilbourne Charrier, Michael Bauers, Clinton, Sam"
output: slidy_presentation 
---

@@

- We have found a noticably large conference gap, with the mean of the old alignment being about -0.32 and the mean of the new alignment being about 2.18.

@@

@@

>>>>

---
title: "Using Monte Carlo to estimate the effects of NHL rule changes"
author: "Kilbourne, Michael, Clinton, Sam"
output: slidy_presentation 
---

@@

- We have found a noticably large conference gap, with the mean of the old alignment being about -0.0202 and the mean of the new alignment being about 2.30.

@@

# What This Shows

- Based on this model we can predict that it is more likely that a team in the West will make the playoffs with a worse overall score than another team in the East much more often than a team in the East will make the playoffs with a worse overall score than another team in the West.

@@

# Sources

- Pettigrew, Stephen. “How the West Will Be Won: Using Monte Carlo Simulations to Estimate the Effects of NHL Realignment.” Journal of Quantitative Analysis in Sports, vol. 10, no. 3, 1 Jan. 2014, 10.1515/jqas-2013-0125. Accessed 10 Dec. 2020.
